Hunting experience shapes individual foraging specialization and predator-prey interactions in an online videogame

### 2023-04-17 manuscript/Chapter2-manuscript.Rmd
document does not rely on pandoc crossref anymore. update equations

---
title: "Hunting experience shapes individual foraging specialization and predator-prey interactions in an online videogame"
output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
    pandoc_args: ["-Fpandoc-crossref"] # to have eq. numbers
bibliography: references2.bib
csl: ecology.csl
---

@@

The full model has the following form, with each equation repeated three times (i.e. one for each level of experience) :

$$
\begin{align}
speed_{pred} &= \text{ } X_{m}\ b_m + M\ env_{m} + N\ av_{m} + Z\ id_{m} + e \\
log(\sigma_{e,\ pred}) &= X_{d}\ b_{d} + Z\ id_{d}
\end{align}
$${#eq:eqn1}

$$
\begin{align}
speed_{prey} &= \text{ } X_{m}\ b_m + M\ env_{m} + N\ av_{m} + Z\ id_{m} + e \\
log(\sigma_{e,\ prey}) &= X_{d}\ b_{d} + Z\ id_{d}
\end{align}
$${#eq:eqn2}

$$
\begin{align}
success_{pred} &= \text{ } X_{m}\ b_m + Z\ id_{m} + e
\end{align}
$${#eq:eqn3}

@@

We parameterized equations (1) and (2) with a Gaussian distribution family (predator and prey speed) and used a beta-binomial distribution family for equation (3) (predator hunting success). We used Gaussian priors for the prey rank ($N(2.5,\ 1)$) and game duration ($N(10,\ 2)$) on the mean part of the model, and the default priors in "brms" for the dispersion part. We used the default Student t priors in "brms" for the intercepts on the mean and dispersion part of the equation. For hunting success, we applied a Gaussian prior on the precision parameter ($N(2,\ 1)$). For every predicted variable, we applied a half-Gaussian on the random effects for the mean part of the model ($N(0,\ 1)$), and the default "brms" Student t prior for the dispersion part of the model.

@@

set_caption(
  tab1,
  caption = "Leave-one-out cross-validation table of the three hierarchical GAMMs relating hunting success to player experience",
  style = "Table Caption"
)

@@

tab2 <- tab2 %>% 
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. We back-transformed the hunting success values, estimated on a logit scale, back to a probability scale.",
      as_sup("\nb "),
      "The intercept values on the mean part of the equation for all traits indicate mean behaviour and success at the population level. The intercept values on the dispersion (i.e. sigma) part of the equation for predator speed indicate behavioural specialization at the population level."
    ),
    ref_symbols = " "
  ) %>%
  font(fontname = "Times New Roman", part = "all") %>%
  width(j = c(2,3,4,5), width = 3.7, unit = "cm") %>%
  width(j = 1, width = 3.2, unit = "cm")

@@

tab3 <- tab3 %>% 
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. All the reported values are standard deviations.",
      as_sup("\nb "),
      "The intercept values on the mean part of the equation for all traits indicate among individual differences in mean behaviour and success.",
      as_sup("\nc "),
      "The intercept values on the dispersion (i.e. sigma) part of the equation for predator speed indicate among individual differences in behavioural specialization. For prey speed and hunting success, they indicate among individual differences in the variability of prey encounters and variability in hunting success, respectively."
    ),
    ref_symbols = " "
  ) %>%
  font(fontname = "Times New Roman", part = "all") %>%
  width(j = c(2,3,4,5), width = 3.7, unit = "cm") %>%
  width(j = 1, width = 3.2, unit = "cm")

>>>>

---
title: "Hunting experience shapes individual foraging specialization and predator-prey interactions in an online videogame"
output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
    #pandoc_args: ["-Fpandoc-crossref"] # to have eq. numbers
bibliography: references2.bib
csl: ecology.csl
---

@@

The full model has the following form, with each equation repeated three times (i.e. one for each level of experience):

```{r model_equations, ft.align = "left"}

# Prepare equations
eqs <- c(
  "speed_{pred} = X_{m}\\ b_{m} + M\\ env_{m} + N\\ av_{m} + Z\\ id_{m} + e",
  "log(\\sigma_{e,pred}) = X_{d}\\ b_{d} + Z\\ id_{d}",
  "speed_{prey} = X_{m}\\ b_{m} + M\\ env_{m} + N\\ av_{m} + Z\\ id_{m} + e",
  "log(\\sigma_{e,prey}) = X_{d}\\ b_{d} + Z\\ id_{d}",
  "success_{pred} = X_{m}\\ b_{m} + Z\\ id_{m} + e"
)
eqs_num <- c(
    "(eqn. 1.1)",
    "(eqn. 1.2)",
    "(eqn. 2.1)",
    "(eqn. 2.2)",
    "(eqn. 3)"
)

# Combine into a dataframe
df <- data.frame(
    formula = eqs,
    number = eqs_num
)

# Create a table to display on Word
ft <- flextable(df)

ft <- compose(
  x = ft, j = 1,
  value = as_paragraph(
    as_equation(formula, height = .5)
  )
)

# Customize table
my_theme <- function(x, ...) {
  x <- colformat_double(x, big.mark = " ",
                        decimal.mark = ".",
                        digits = 2)
  x <- border_remove(x)
  x <- delete_part(x, part = "header")
  x <- align(x, j = 1, align = "left", part = "body")
  x <- align(x, j = 2, align = "right", part = "body")
  x <- font(x, fontname = "Times New Roman", part = "body")
  x <- fontsize(x, size = 12, part = "body")
  x <- width(x, j = 1, width = 10, unit = "cm")
  x <- width(x, j = 2, width = 6.51, unit = "cm")
}

ft <- my_theme(x = ft)
ft

@@

We parameterized equations 1.1 to 2.2 with a Gaussian distribution family (predator and prey speed) and used a beta-binomial distribution family for equation 3 (predator hunting success). We used Gaussian priors for the prey rank ($N(2.5,\ 1)$) and game duration ($N(10,\ 2)$) on the mean part of the model (equations 1.1, 2.1, and 3), and the default priors in "brms" for the dispersion part (equations 1.2 and 2.2). We used the default Student t priors in "brms" for the intercepts on the mean and dispersion part of the model. For hunting success, we applied a Gaussian prior on the precision parameter ($N(2,\ 1)$). For every predicted variable, we applied a half-Gaussian prior ($N(0,\ 1)$) on the random effects for the mean part of the model (equations 1.1, 2.1, and 3), and the default "brms" Student t prior for the dispersion part of the model (equations 1.2 and 2.2).

@@

set_caption(
  tab1,
  caption = "Leave-one-out cross-validation table of the three hierarchical GAMMs relating hunting success to player experience",
  style = "Table Caption"
)
```

@@

tab2 <- tab2 %>% 
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. We back-transformed the hunting success values, estimated on a logit scale, back to a probability scale.",
      as_sup("\nb "),
      "The intercept values on the mean part of the equation for all traits indicate mean behaviour and success at the population level. The intercept values on the dispersion (i.e. sigma) part of the equation for predator speed indicate behavioural specialization at the population level."
    ),
    ref_symbols = " "
  ) %>%
  font(fontname = "Times New Roman", part = "all") %>%
  width(j = c(2, 3, 4, 5), width = 3.7, unit = "cm") %>%
  width(j = 1, width = 3.2, unit = "cm")

@@

tab3 <- tab3 %>% 
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. All the reported values are standard deviations.",
      as_sup("\nb "),
      "The intercept values on the mean part of the equation for all traits indicate among individual differences in mean behaviour and success.",
      as_sup("\nc "),
      "The intercept values on the dispersion (i.e. sigma) part of the equation for predator speed indicate among individual differences in behavioural specialization. For prey speed and hunting success, they indicate among individual differences in the variability of prey encounters and variability in hunting success, respectively."
    ),
    ref_symbols = " "
  ) %>%
  font(fontname = "Times New Roman", part = "all") %>%
  width(j = c(2, 3, 4, 5), width = 3.7, unit = "cm") %>%
  width(j = 1, width = 3.2, unit = "cm")
